6CCS3PRJ \\\vspace{0.5cm} A Pragmatic Infrastructure Modelling and Verification Framework

### 2014-04-22 paper.tex
More Steffen fixes

Nagios is an open source infrastructure and application monitoring framework. Often considered the `industry standard', it provides a vast array of features, from execution of fine-grained protocol specific tests to complex capacity planning forecasts. It is also very extensible, which is perhaps the largest reason for its success within the industry.

@@

This collection of tools all work together in providing near real-time metrics tracking and graphing, they are used heavily at vastly successful startups such as 37signals, GitHub and Shopify. Metrics can be collected from the infrastructure and application layers. 
CollectD is a system utility written in C that periodically makes system calls to extract performance fundamentals such as CPU, memory and network usage.

\label{StatsD}
Application level metrics can be collected using StatsD. Applications can send metrics to a local StatsD instance via UDP, which adds very little performance overhead. This means that it is possible to heavily instrument the critical paths of an application except in extremely performance sensitive scenarios. Both of these tools aggregate this data and flush it to a backend Graphite instance at configurable intervals. Graphite provides extremely flexible data visualisation techniques, but requires some up front investment in time to produce meaningful results.

@@

\subsubsection{New Relic - APM} 
New Relic is a popular subscription-based, hosted Application Performance Monitoring (APM) service. It provides integration with popular languages, frameworks and platforms such as the Java Virtual Machine (JVM), Ruby/Ruby on Rails and Python with the Django web framework.

@@

@@

\paragraph{Speed/Ease of Setup} Many comments from developers detailed the fact that most monitoring and modelling tools were too time consuming to set up, and clients did not see demonstrable value in investing time upfront in this process before services were launched and issues actually occurred.

@@

\paragraph{Simplicity and Pragmatism} Often the need for extensive application and infrastructure monitoring is not recognised until after the application has been deployed into a production environment. Introducing monitoring at an earlier stage, e.g.. in a staging environment, can highlight issues of reliability and performance before they are experienced in production. Monitoring key domain specific metrics can also aid in reasoning about the runtime behaviour of the system. With these benefits in mind, the tool should be simple enough to introduce early in the development process with minimal effort on the part of the developer, it should provide pragmatic value from the start, and offer the flexibility to continue to deliver value as the system grows in complexity.

@@

Maintaining agility while providing a suitable quality of service is challenging. Continuous Integration (CI) and Delivery (CD) are fundamental principles of the Extreme Programming (XP) movement and discuss solutions to this problem at great length, the most cited benefit is the reduction of risk. Small amounts of change applied frequently are easier to reason about and test, and of course provide the end user with value quicker. In conjunction with version control systems, CI/CD can be used to effectively identify the root cause of problems soon after they occur. The application of CI/CD is widespread within the industry, and a whole suite of tools such as CI servers, automated code deployment tools and configuration management utilities all aid to facilitate the practice.

@@

Due to its meta-programming features and flexibility in syntax, Ruby is somewhat uniquely amenable to creating domain specific languages within the language itself, so called `internal DSLs'.

@@

\begin{enumerate}
  \item{Detection of Operating System} - The tool initially supports Linux and Mac OS X only, it will distinguish between these operating systems or abort the installation if running on a different platform.
  \item{Detection or Installation of Ruby} - If Ruby 2.0.1 is not installed, the script will use the standard package manager of the distribution to install it.
  \item{Download of Agent Software} - The source code will be obtained directly from GitHub over a secure connection protecting against spoofing attacks, dependencies will be resolved and installed.
  \item{Host Registration} - Optionally, the host can be registered with the management server, the hostname and IP address as well as an optional service name and environment will be passed to the management server. This is appropriate on servers but not development workstations.
\end{enumerate}

@@

\pagebreak
\subsection{Hosts}
Hosts are a simple structure, they are conceptually just an instance of the management agent running on a physical or virtual server. When the management software is installed, the user can specify an environment, e.g.\ development, staging or production. Hosts are initially registered via the `setup' command of the management agent, and are associated/dissociated with services when the `start' and `stop' monitoring commands are used, specifying a particular service specification. Hosts are considered transient, they are instances of an application running at a particular time. This is particularly true of more dynamic infrastructure such as auto-scaling groups.

@@

The changes feed is implemented as a Server Sent Events (SSE) stream, SSE is a HTML5 standard for uni-directional, long running HTTP responses. Alternatives to Server Sent Events are WebSockets and standard long polling techniques. SSE was chosen over WebSockets for the following reasons:

@@

\begin{figure}[h]
\includegraphics[scale=0.6]{email.png}
\caption{An example email notification, triggered when an incident has been detected.}
\end{figure}

>>>>

Nagios\footnote{Nagios - http://www.nagios.org/} is an open source infrastructure and application monitoring framework. Often considered the `industry standard', it provides a vast array of features, from execution of fine-grained protocol specific tests to complex capacity planning forecasts. It is also very extensible, which is perhaps the largest reason for its success within the industry.

@@

This collection of tools all work together in providing near real-time metrics tracking and graphing, they are used heavily at vastly successful startups such as 37signals~\cite{37SignalsGraphite} and Etsy~\cite{EtsyGraphite}. Metrics can be collected from the infrastructure and application layers.

\label{StatsD}
Application level metrics can be collected using StatsD\footnote{StatsD - http://codeascraft.com/2011/02/15/measure-anything-measure-everything/}. Applications can send metrics to a local StatsD instance via UDP, which adds very little performance overhead. This means that it is possible to heavily instrument the critical paths of an application except in extremely performance sensitive scenarios. Both of these tools aggregate this data and flush it to a backend Graphite\footnote{Graphite - https://graphite.readthedocs.org/en/latest/overview.html} instance at configurable intervals. Graphite provides extremely flexible data visualisation techniques, but requires some up front investment in time to produce meaningful results.

@@

\subsubsection{New Relic - APM} 
New Relic\footnote{New Relic - http://newrelic.com/about} is a popular subscription-based, hosted Application Performance Monitoring (APM) service. It provides integration with popular languages, frameworks and platforms such as the Java Virtual Machine (JVM), Ruby/Ruby on Rails and Python with the Django web framework.

@@

The following chapter details the design and implementation process. It specifically focuses on the the critical technical decisions made, and how they relate back to the requirements and design objectives set out initially.

@@

\paragraph{Speed/Ease of Setup} Comments from developers often mention that most monitoring and modelling tools were too time consuming to set up. Clients did not see demonstrable value in investing time upfront in this process before services were launched and issues actually occurred.

@@

\paragraph{Simplicity and Pragmatism} Often the need for extensive application and infrastructure monitoring is not fully recognised until after the application has been deployed into a production environment. Introducing monitoring at an earlier stage, e.g.. in a staging environment, can highlight issues of reliability and performance before they are experienced in production. Monitoring key domain specific metrics can also aid in reasoning about the runtime behaviour of the system. With these benefits in mind, the tool should be simple enough to introduce early in the development process with minimal effort on the part of the developer, it should provide pragmatic value from the start, and offer the flexibility to continue to deliver value as the system grows in complexity.

@@

Maintaining agility while providing a suitable quality of service is challenging. Continuous Integration (CI) and Delivery (CD) are fundamental principles of the Extreme Programming\cite{BeckXP} (XP) movement and discuss solutions to this problem at great length, the most cited benefit is the reduction of risk. Small amounts of change applied frequently are easier to reason about and test, and of course provide the end user with value quicker. In conjunction with version control systems, CI/CD can be used to effectively identify the root cause of problems soon after they occur. The application of CI/CD is widespread within the industry, and a whole suite of tools such as CI servers, automated code deployment tools and configuration management utilities all aid to facilitate the practice.

@@

Due to its meta-programming features and flexibility in syntax, Ruby is somewhat uniquely amenable to creating domain specific languages within the language itself, so called `internal DSLs'\footnote{Internal/Embedded DSL's - http://www.martinfowler.com/bliki/DomainSpecificLanguage.html}.

@@

\begin{enumerate}
  \item{Detection of Operating System} - The tool initially supports Linux and Mac OS X only, it will distinguish between these operating systems or abort the installation if running on a different platform.
  \item{Detection or Installation of Ruby} - If Ruby 2.0 or higher is not installed, the script will use the standard package manager of the distribution to install it.
  \item{Download of Agent Software} - The source code will be obtained directly from GitHub over a secure connection protecting against spoofing attacks, dependencies will be resolved and installed.
  \item{Host Registration} - Optionally, the host can be registered with the management server, the hostname and IP address as well as an optional service name and environment will be passed to the management server. This is appropriate on servers but not development workstations, as these are irrelevant to the system under test.
\end{enumerate}

@@

\pagebreak
\subsection{Hosts}
Hosts are a simple structure, they are conceptually just an instance of the management agent running on a physical or virtual server. When the management software is installed, the user can specify an environment, e.g.\ development, staging or production.

Hosts are initially registered via the `setup' command of the management agent, and are associated/dissociated with services when the `start' and `stop' monitoring commands are used, specifying a particular service specification. Hosts are considered transient, they are instances of an application running at a particular time. This is particularly true of more dynamic infrastructure such as auto-scaling groups.

@@

The changes feed is implemented as a Server Sent Events\footnote{HTML5 Server Sent Events - http://www.w3.org/TR/2009/WD-eventsource-20091029/} (SSE) stream, SSE is a HTML5 standard for uni-directional, long running HTTP responses. Alternatives to Server Sent Events are WebSockets and standard long polling techniques. SSE was chosen over WebSockets for the following reasons:

@@

\begin{figure}[h]
  \centering
  \includegraphics[scale=0.6]{email.png}
  \caption{An example email notification, triggered when an incident has been detected.}
\end{figure}
